A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-25 shanghai.tex
Finished the proof of restriction of scalars over local fields. Yay!
Can you confirm Equation 14?

DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
local Langlands correspondence \cite{reeder-debacker:09a}.  
After developing Deligne-Luzstig representations, 
the next step Lusztig took in studying representations
of finite groups of Lie type was to introduce character sheaves for reductive groups over $\Fq$.
We hope that our quasicharacter sheaves can provide a stepping stone to a similar theory for
representations of $p$-adic groups.

@@

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{deligne:SGA4.5}*{sommes trig.} and many people have since referred to such objects
as character sheaves; see for example, \cite{kamgarpour:09a}. 
%\cite{boyarshenko-drinfeld:motivated}*{\S 1.8}.  
Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
is a direct generalization of the sheaf--function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The main use
of the term character sheaf is due to Lusztig: it is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in \cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups over algebraically closed fields with cyclic component groups in the series of papers beginning with \cite{lusztig:disconnected1}.  
When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.

@@

In Section~\ref{sec:GN} we review the Greenberg transform of N\'eron models of tori, which produces
group schemes over $\Fq$ from algebraic tori $T$ over $K$.
Section~\ref{sec:bdchar} then uses Theorem~\ref{thm:snake} to give a geometrization of characters of $T$
of bounded depth.
We give a reinterpretation of this result in Section~\ref{sec:quasichar}, using a limit process to simultaneously
geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar}, \ref{sec:quasichar} and \ref{sec:wrK} also include
functoriality results that we hope to use in a future discussion of class field theory.
In Section~\ref{sec:transfer} we discuss a transfer principle which allows
a geometric transfer of characters between characteristic $p$ tori and characteristic $0$ tori.
We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over non-archimedean local fields.

@@

To define the category of finite quasicharacter sheaves we must work a bit harder.
Consider the following category $C(G)$.
Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a a finite, surjective
\'etale morphism and a morphism of commutative group $\Fq$-schemes, for which
the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
An object in $C(G)$ is a pair $(f,\psi)$ where: 
$f : H\to G$ is a discrete isogeny 
and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$ 
where $\alpha$ is a morphism of schemes such that $f' = f\circ \alpha$
and $T : V\to V'$ is a linear transformation equivariant 
for the action of $\ker f'$ on $V'$ by $\psi'$ 
and the action of $\ker '$ on $V$ by $\psi \circ \alpha$.
\[
\begin{tikzcd}
V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
V' & \Aut(V) & \arrow[swap]{l}{\psi} \arrow[swap]{u}{\alpha\vert_{\ker f}} \ker f \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G
\end{tikzcd}
\]
We say that $(\alpha,T)$ in $C(G)$ is a \emph{weak isomorphism} if $\alpha$ is surjective
and $T$ is an isomorphism of vector spaces.
Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.

@@

The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$.
%\Clifton{Do you think I should say more about $P_{n}$?}
%\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
\Clifton{I took the reference to BLR for $P_n$ out, because it didn't actually give any information. 
This must be in DG, but I don't have a copy.}
For a given Néron model $\TT$ of $T$, set
\[
\GN{T}_n \ceq \Gr_n(\TT)
\qquad \text{and}\qquad
f_n \ceq P_n(\TT).
\]

Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
 \begin{enumerate}
   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
  \labitem{(GN.1)}{smooth} 
  $\GN{T}_n$ is a smooth commutative group scheme locally of finite type over $\Fq$ 
  and the component group of $\GN{T}_n$ is geometrically finitely generated. 
  Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction. 
  Since smoothness is preserved under base change, 
  $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ 
  is a smooth group scheme over an Artinian ring with perfect residue field. 
  The Greenberg functor preserves smoothness, 
  so $\GN{T}_n$ is a smooth group scheme locally of finite type over $\Fq$. 
  The Greenberg functor takes the geometric identity component of $\TT_n$ 
  to the geometric identity component of $\GN{T}_n$;
  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
  this group is finitely generated by \cite{xarles:93a}*{2.18}.
  \labitem{(GN.2)}{truncation}
  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a morphism of group schemes over $\Fq$. 
  This follows from the fact that $P_{n}$ is a natural transformation between additive functors.
  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
\end{enumerate}

\begin{definition}
The \emph{Greenberg transform of the N\'eron model of $T$} is the pro-group scheme over $\Fq$ given by $\cdef{\GN{T}} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$ (with reference to the morphisms $f_n : \GN{T}_{n+1} \to \GN{T}_n$).
\end{definition}

If $K = \mathbb{Q}_q$ and $T = \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, the group $\FF_q$-scheme of units in the ring scheme $\mathbb{W}_{\FF_q}$.

@@

  The definition of $F_1$ depends 
  on the choice of a Néron model for every algebraic torus $T$.
  However, since Néron models are unique up to unique isomorphism,
  the isomorphism class of $\GN{T}_n$ is uniquely determined by $T$
  \Clifton{Hmmm}
  and the group of isomorphism classes of objects in $\QC(\GN{T}_n)$ 
  is uniquely determined by $T$. 
  To define $F_1$ on objects, one uses the Néron mapping property.

  Finally, we show that $\trFrob{T,n}$ is functorial.
The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
while the second part shows that Trace of Frobenius is a natural transformation
$t: F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a
natural transformation between additive functors.
\end{proof}

@@

For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
Note that $f_{n\leq m}:  \GN{T}_{m} \to \GN{T}_{n}$ is a morphism of group schemes over $\Fq$.
Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor produced by applying Proposition~\ref{prop:pullback} to $f_{n\leq m}$.
We now define a category which allows us to extend the notion of quasicharacter sheaf to the pro-group scheme $\GN{T}$.

\begin{definition}
An object in $\QC(\GN{T})$ is an equivalence class in $\cup_{n} \obj \QC(\GN{T}_n)$ under the relation: $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$. Objects in $\QC(\GN{T})$ all take the form
\[
[\qcs{L}_n] \ceq \{ f_{n\leq k}^* \qcs{L}_n \tq n\leq k\},
\]
for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to $\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$. Maps in $\QC(\GN{T})$ all take the form
\[
[\alpha_k] \ceq \{ f_{k\leq i}^* \alpha_k \tq k\leq i\},
\]
for some unique $\alpha_k \in \QC(\GN{T}_k)$.
Identities and composition are defined in the natural way.
Category $\QC(\GN{T})$ carries a tensor structure under
\[
[\qcs{L}_n]\otimes [\qcs{L}_m] \ceq [f_{n\leq k}^*\qcs{L}_n \otimes f_{m\leq k}^*\qcs{L}_m],
\qquad k = \max\{ n,m\}.
\]
Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
We refer to objects in the rigid symmetric monoidal category $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
\end{definition}

@@

\begin{proof}
Observe that $\QC(\GN{T})$ comes equipped with monoidal subcategories
\[
\begin{tikzcd}
\ & & & \QC(\GN{T})\\
\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & 
\end{tikzcd}
\]
defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
Passing to isomorphism classes of objects and invoking the universal property of $\varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d}$ gives a group homomorphism
$\theta: \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \to \QCiso{\GN{T}}$; this is a bijection 
with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
Now use Theorem~\ref{thm:application}.
\end{proof}

\section{Weil restriction for local fields}
\label{sec:wrK}

As indicated in the Introduction, we are tantalized 
by the idea that quasicharacter sheaves for $T$ 
may play a key role in a new geometric, categorial version 
of the local Langlands correspondence for algebraic tori 
over non-archimedean local fields. 
As with the local Langlands correspondence for algebraic tori over local fields, 
it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
provided that the category of quasicharacter sheaves behaves properly with regard to
Weil restriction; see \cite{yu:09a}*{Thm 7.5 (2)}. 
The next proposition shows that the category of quasicharacter sheaves for 
algebraic tori does indeed behave properly with regard to Weil restriction.

\begin{proof}
First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
is a scheme over $\OK$, 
the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
is obtained by base change along $\OK \to \OK/\pK^n$ 
followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
see Definition~\ref{def:Grn}. 
Note also that 
\begin{equation}\label{nem}
\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
\end{equation}

\begin{proposition}\label{prop:wrK}
Let $K'/K$ be a finite Galois extension; 
let $k'/k$ be the corresponding finite Galois extension of residue fields.
Let $T$ be an algebraic torus over $K$ and 
set $T' = T \times_\Spec{K} \Spec{K'}$.
The natural inclusion 
\[
T \hookrightarrow \Res_{K'/K} T' =: T''
\]
induces a map of $k$-schemes
$\GN{T} \hookrightarrow \GN{T}''$
and thus a functor on quasicharacter sheaves through pullback:
\begin{equation}\label{eq:wrK}
\QC(\GN{T}'') \to \QC(\GN{T}).
\end{equation}
Through trace of Frobenius, this functor induces the homomorphism
\[
\begin{tikzcd}[column sep=60]
\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
\end{tikzcd}
\]  
\end{proposition}

\begin{proof}
Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} for lft-Neron models
gives a canonical isomorphism 
\begin{equation}\label{weilneron}
\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
\end{equation}
By Lemma~\ref{lemma:wrK}, 
\begin{equation}\label{weilgreenberg}
\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
\iso
\Res_{k'/k} \Gr_{en}(\underline{T'}).
\end{equation}
This gives
\[
\GN{T}''_n \iso \Res_{k'/k} \GN{T}'_{en}.
\]
\Clifton{Now I'm stuck here.}
But
\[
\GN{T}'_{en} = \Gr_{en}(\underline{T'}) = \Gr_{en}(\underline{T}\times_{\OK} {\mathcal{O}_{K'}}) \iso . . . 
\]
Now use Proposition~\ref{prop:csbe}.
\end{proof}

@@

>>>>

DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
local Langlands correspondence.% \cite{reeder-debacker:09a}.  
After developing Deligne-Lusztig representations, 
the next step Lusztig took in studying representations
of finite groups of Lie type was to introduce character sheaves for reductive groups over $\Fq$.
We hope that our quasicharacter sheaves can provide a stepping stone to a similar theory for
representations of $p$-adic groups.

@@

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{deligne:SGA4.5}*{sommes trig.} and many people have since referred to such objects
as character sheaves; see for example, \cite{kamgarpour:09a}. 
%\cite{boyarshenko-drinfeld:motivated}*{\S 1.8}.  
Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
is a direct generalization of the sheaf--function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The main use
of the term character sheaf is of course due to Lusztig. It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in \cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups over algebraically closed fields with cyclic component groups in the series of papers beginning with \cite{lusztig:disconnected1}.  
When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.

@@

In Section~\ref{sec:GN} we review the Greenberg transform of N\'eron models of tori, which produces
group schemes over $\Fq$ from algebraic tori $T$ over $K$.
Section~\ref{sec:bdchar} then uses Theorem~\ref{thm:snake} to give a geometrization of characters of $T$
of bounded depth.
We give a reinterpretation of this result in Section~\ref{sec:quasichar}, using a limit process to simultaneously
geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar}, \ref{sec:quasichar} and \ref{sec:wrK} also include
functoriality results that we hope to use in a future discussion of 
local class field theory.
In Section~\ref{sec:transfer} we discuss a transfer principle which allows
a geometric transfer of characters between characteristic $p$ tori and characteristic $0$ tori.
We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over local fields.

@@

To define the category of finite quasicharacter sheaves we must work a bit harder.
Consider the following category $C(G)$.
Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a finite, surjective
\'etale morphism and a morphism of commutative group $\Fq$-schemes, for which
the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
An object in $C(G)$ is a pair $(f,\psi)$ where: 
$f : H\to G$ is a discrete isogeny 
and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$ 
where $\alpha$ is a morphism of schemes such that $f' = f\circ \alpha$
and $T : V\to V'$ is a linear transformation equivariant 
for the action of $\ker f'$ on $V'$ by $\psi'$ 
and the action of $\ker '$ on $V$ by $\psi \circ \alpha$.
\[
\begin{tikzcd}
V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
V' & \Aut(V) & \arrow[swap]{l}{\psi} \arrow[swap]{u}{\alpha\vert_{\ker f}} \ker f \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G
\end{tikzcd}
\]
We say that $(\alpha,T)$ in $C(G)$ is a \emph{weak isomorphism} if $\alpha$ is surjective
and $T$ is an isomorphism of vector spaces.
Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.

@@

The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
For a given Néron model $\TT$ of $T$, set
\[
\GN{T}_n \ceq \Gr_n(\TT)
\qquad \text{and}\qquad
f_n \ceq P_n(\TT).
\]

Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
 \begin{enumerate}
   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
  \labitem{(GN.1)}{smooth} 
  $\GN{T}_n$ is a smooth commutative group scheme locally of finite type over $\Fq$ 
  and the component group of $\GN{T}_n$ is geometrically finitely generated. 
  Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction. 
  Since smoothness is preserved under base change, 
  $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ 
  is a smooth group scheme over an Artinian ring with perfect residue field. 
  The Greenberg functor preserves smoothness, 
  so $\GN{T}_n$ is a smooth group scheme locally of finite type over $\Fq$. 
  The Greenberg functor takes the geometric identity component of $\TT_n$ 
  to the geometric identity component of $\GN{T}_n$;
  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
  this group is finitely generated by \cite{xarles:93a}*{2.18}.
  \labitem{(GN.2)}{truncation}
  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$; 
  see  \cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}
  and  \cite{stasinski:12a}*{\S 4}.
  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
\end{enumerate}

@@

  The definition of $F_1$ depends 
  on the choice of a Néron model for every algebraic torus $T$.
  However, since Néron models are unique up to unique isomorphism,
  the isomorphism class of $\GN{T}_n$ is uniquely determined by $T$
  \Clifton{Hmmm}
  and the group of isomorphism classes of objects in $\QC(\GN{T}_n)$ 
  is uniquely determined by $T$. 
  To define $F_1$ on morphisms one uses the Néron mapping property.

  Finally, we show that $\trFrob{T,n}$ is functorial.
The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
while the second part shows that Trace of Frobenius is a natural transformation
$t_{ - ,n} : F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
we see that $F_1$ is an additive functor and $t_{ - ,n}: F_1 \to F_2$ is a
natural transformation between additive functors.
\end{proof}

@@

\begin{definition}\label{def:objGN}
The \emph{Greenberg transform of the N\'eron model of $T$} 
is the pro-group scheme over $\Fq$ given by 
$\cdef{\GN{T}} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$, 
with reference to the family of  surjective morphisms of 
$\Fq$-group schemes $f_n : \GN{T}_{n+1} \to \GN{T}_n$.
\end{definition}

\begin{remark}
If $K = \mathbb{Q}_q$ and 
$T = \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, 
the group scheme (!) over $\Fq$ of units in the ring scheme $\mathbb{W}_{\FF_q}$
and $\GN{T}$, as a scheme, is the disjoint union of copies of $\mathbb{W}^*_{\FF_q}$
indexed by the integers. Based on this example, 
we ask if, for arbitrary $T$, the pro-group scheme $\GN{T}$ is, in fact, a group scheme.
We have not explored that question.
\end{remark}

For any  ordered pair of positive integers $n< m$ define 
$f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ 
by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; 
also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
Note that $f_{n\leq m}:  \GN{T}_{m} \to \GN{T}_{n}$ is a surjective morphism 
of group schemes over $\Fq$.
Let 
\[
f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})
\]
be the functor produced by applying Proposition~\ref{prop:pullback} to $f_{n\leq m}$.
We now define a category which allows us to extend the notion 
of quasicharacter sheaf to the pro-group scheme $\GN{T}$.

\begin{definition}\label{def:catGN}
An object in $\QC(\GN{T})$ is an equivalence class in 
$\cup_{n\in\ZZ_{>0}} \obj \QC(\GN{T}_n)$ under the relation: 
$\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ 
if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$. 
Objects in $\QC(\GN{T})$ all take the form
\[
[\qcs{L}_n] \ceq \{ f_{n\leq k}^* \qcs{L}_n \tq n\leq k\},
\]
for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes 
in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ 
under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to 
$\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$. 
Maps in $\QC(\GN{T})$ all take the form
\[
[\alpha_k] \ceq \{ f_{k\leq i}^* \alpha_k \tq k\leq i\},
\]
for some unique $\alpha_k \in \QC(\GN{T}_k)$.
Identities and composition are defined in the natural way.
Category $\QC(\GN{T})$ carries a tensor structure under
\[
[\qcs{L}_n]\otimes [\qcs{L}_m] \ceq [f_{n\leq k}^*\qcs{L}_n \otimes f_{m\leq k}^*\qcs{L}_m],
\qquad k = \max\{ n,m\}.
\]
Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
We refer to objects in the rigid symmetric monoidal category 
$\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} 
or \emph{quasicharacter sheaves for $T$}.
\end{definition}

@@

\begin{proof}
Observe that $\QC(\GN{T})$ comes equipped with monoidal subcategories
\[
\begin{tikzcd}
\ & & & \QC(\GN{T})\\
\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & 
\end{tikzcd}
\]
defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, 
for all positive integers $n\leq m$.
Passing to isomorphism classes of objects and invoking the 
universal property of $\varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n}$ 
gives a group homomorphism
$\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$; 
this is a bijection  with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
Now use Theorem~\ref{thm:application} and Proposition~\ref{prop:pullback} 
and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$ 
with reference to the family of group homomorphisms 
dual to $f_{n} : \GN{T}_{n+1}(\Fq) \to \GN{T}_n(\Fq)$.
\end{proof}

@@

\section{Restriction of scalars over local fields}
\label{sec:wrK}

As indicated in the Introduction, we are tantalized 
by the idea that quasicharacter sheaves for $T$ 
may play a key role in a new geometric, categorial version 
of the local Langlands correspondence for algebraic tori 
over non-archimedean local fields. 
As with the local Langlands correspondence for algebraic tori over local fields, 
it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
provided that the category of quasicharacter sheaves behaves properly with regard to
Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
The next proposition shows that the category of quasicharacter sheaves for 
algebraic tori does indeed behave properly with regard to Weil restriction.

\begin{proof}
First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
is a scheme over $\OK$, 
the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
is obtained by base change along $\OK \to \OK/\pK^n$ 
followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
see Definition~\ref{def:Grn}. 
Note also that 
\Clifton{I haven't checked this! Have you?}
\begin{equation}\label{nem}
\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
\end{equation}

\begin{proposition}\label{prop:wrK}
Let $K'/K$ be a finite Galois extension and
let $k'/k$ be the corresponding finite Galois extension of residue fields.
Let $T$ be an algebraic torus over $K$ and 
set $T' = T \times_\Spec{K} \Spec{K'}$.
The canonical closed immersion $T \hookrightarrow \Res_{K'/K} T'$
induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which, through the pull-back functor and the trace of Frobenius, induces the homomorphism
\[
\begin{tikzcd}[column sep=60]
\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
\end{tikzcd}
\]  
\end{proposition}

\begin{proof}
Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to lft-Néron models
we see that a Néron model for $\Res_{K'/K}(T')$ is $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$;
see also the proof of \cite{xarles:93a}*{Lemma 2.6}.
By the Néron mapping property, the canonical closed immersion $T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism $\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
Applying the Greenberg transform $\Gr_{n}$ to this morphism
and using Lemma~\ref{lemma:wrK} defines the morphism of $\Fq$-group schemes
\begin{equation}\label{men}
\GN{T}_n \to \Res_{k'/k} \GN{T}'_{en}.
\end{equation}
Passing to the pro-group schemes in Definition~\ref{def:objGN} 
the family of morphisms \eqref{men} determines a morphism of pro-group schemes
\[
\GN{T} \to \Res_{k'/k} \GN{T}'.
\]
Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$, the pull-back functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$ obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
\[
\Hom_{< en}(T'(K'),\EEx) \to \Hom_{< n}(T(K),\EEx).
\]
Passing to inverse limits defines
\[
\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
\]
Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
\end{proof}
